Modal Abstractions for Virtualizing Memory Addresses

### 2023-11-15 examples.tex
p2v stuff

\begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,\Xi,m) \ast \\
  \qquad\qquad\qquad \bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, paddr})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, paddr})} \\
  \qquad\qquad\qquad \bigast{(\vaddr, \textsf{paddr})\in \Xi}{\exists\; (\textsf{qfrac, val, vaddr}) \ldotp \ulcorner \textsf{vaddr} = \textsf{paddr} + \textsf{KERNBASE} \urcorner \ast  \underbrace{\sumwalkabs\vaddr\qfrac\paddr }_\text{Ghost translation} \ast \\
\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad    \underbrace{\paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\}\; \vale}_\text{Physical location} \ast \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner }\\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
   \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \\ \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad \ownGhost\gammaPred{\authfull{\ptableabswalk\Xi}}

@@

;; This offsetst physical address at KERNBASE!
add r,  

>>>>

\newcommand{\true}{\textsf{true}}
\tikzstyle{boxedassert_border} = [sharp corners,line width=0.2pt]
\NewDocumentCommand \boxedassertpv {O{} m o}{%
	\tikz[baseline=(m.base)]{
		%	  \node[rectangle, draw,inner sep=0.8pt,anchor=base,#1] (m) {${#2}\mathstrut$};
		\node[rectangle,inner sep=1.5pt,outer sep=0.2pt,anchor=base] (m) {${\,#2\,}\mathstrut$};
		\draw[#1,boxedassert_border] ($(m.south west)$) rectangle ($(m.north east)$);
	}\IfNoValueF{#3}{^{\,#3}}%
}
\newcommand*{\knowInvpv}[2]{\boxedassertpv{#2}[#1]}
\newcommand*{\ownGhostpv}[2]{\boxedassertpv[dash dot]{#2}[#1]}

\newcommand{\sumpv}[3]{
  \ownGhostpv\gammaPred{\authfrag{\singletonMap{#1}{(#2, #3)}}}
}

\newcommand{\pvmapping}[1]{\mathcal{A}\textsf{PVMappings}(#1)}
\newcommand{\sumapacesfull}[2]{
  \ownGhost\gammaPreds{\authfull{\singletonMap{#1}{#2}}}
}
\begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,\Xi,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,\Xi,m) \ast \\
  \qquad\qquad\qquad \bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, paddr})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, paddr})} \\
  \qquad\qquad\qquad \bigast{(\textsf{paddr}) \in \Xi}{\exists\; (\textsf{qfrac, val, vaddr}) \ldotp \ulcorner \textsf{vaddr} = \textsf{paddr} + \textsf{KERNELBASE} \urcorner \ast  \underbrace{\sumwalkabs\vaddr\qfrac\paddr }_\text{Ghost translation} \ast \\
\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad    \underbrace{\paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\}\; \vale}_\text{Physical location} \ast \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner }\\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
   \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \\ \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad \ownGhostpv\gammaPred{\authfull{\pvmapping\Xi}}

@@

\begin{figure}\footnotesize
\begin{lstlisting}[mathescape]
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\Xi,m) \ast \ulcorner \textsf{KERNELBASE} + \fpaddr > 0 \urcorner }_{\rtv}$
$\specline{ \texttt{rip}\mapsto_{\textsf{r}} \textsf{iv} \ast \texttt{rflags}\mapsto_{\textsf{r}} \textsf{flaglist} \ast \texttt{rbx}\mapsto_{\textsf{r}} \fpaddr  }_{\rtv}$
$\specline{ \sumapaces\rtv\delta  \ast \sumwalkabs\vaddr\qfrac\fpaddr \ast \sumpv\fpaddr\qfrac\true  }_{\rtv}$
;; This offsetst physical address at KERNELBASE!
add rbx, KERNELBASE
$\specline{\exists \textsf{flaglistadd, qphysical, q0, w, flaglistadd, val}, \textsf{P} \ast \texttt{rip}\mapsto_{\textsf{r}} \textsf{iv+7} \ast \texttt{rflags}\mapsto_{\textsf{r}} \textsf{flaglistadd} \ast \texttt{rbx}\mapsto_{\textsf{r}} \fpaddr + \textsf{KERNELBASE} }_{\rtv}$
$\specline{\bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, } \fpaddr)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, \fpaddr})}}_{\rtv}$
$\specline{\mathcal{R} -\ast \bigast{(\fpaddr) \in \Xi}{\exists\; (\textsf{qfrac, val, vaddr}) \ldotp \ulcorner \textsf{vaddr} = \fpaddr + \textsf{KERNELBASE} \urcorner \ast \sumwalkabs\vaddr\qfrac\fpaddr  \ast \paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\} \; \vale\ast  \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner}}_{\rtv}$
$\specline{ \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \ownGhostpv\gammaPred{\authfull{\pvmapping\Xi}}}$
$\specline{ \sumapaces\rtv\delta  \ast\sumwalkabs\vaddr\qfrac\fpaddr \ast \sumpv\fpaddr\qfrac\true \ast \textsf{P}}_{\rtv}$
$\specline{\vaddr \mapsto_{\texttt{vpte}} \{\textsf{q}, \textsf{qfrac}\} \paddr \;(\texttt{val})}$
\end{lstlisting}
\caption{Identity mapping of a physical address to a virtual one.}
\label{fig:mapping_code}
\end{figure}
